### 2014-08-04 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update
Chicago: Minor edit to units/symbols

@@

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    &  k: 0.12 \; \si{W/(m.K)})                                     & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
                                   &  c$_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  &  k: 0.28 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
                                   &  c$_{p}$: 1.0 \; \si{kJ/(kg.K)}                              & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\chapter{List of Symbols}

\begin{tabbing}
\hspace{1.5in} \= \\
ft \> foot \\
m \> meter \\
min \> minute \\
Pa \> Pascal \\
psi \> pound per square inch \\
s \> second \\
W \> Watt \\
$k$ \> thermal conductivity \\
$\rho$ \> density \\
$c_{p}$ \> specific heat \\
\end{tabbing}

@@

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    &  $k$: 0.12 \; \si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
                                   &  $c_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  &  $k$: 0.28 \; \si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
                                   &  $c_{p}$: 1.0 \; \si{kJ/(kg.K)}                               & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
